Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-03-04 paper/main.tex
section 5 polished

The presented reduction algorithms have been implemented in a tool called
\telatko. It uses the Spot library~\cite{duret.16.atva2} for automata parsing
and manipulation, and the Z3 Theorem Prover~\cite{demoura.08.tacas} to solve
the satisfiability of QBF formulas. \telatko is implemented in Python
and has a CLI interface which allows users to specify details about a run. The tool expects file containing automata in HOA format ~\cite{babiak.15.cav} and processes the input file, the result is saved in the specified output file again in HOA format. If there is no output file given, \telatko prints the result to $\mathit{stdout}$. 
The switch \texttt{-L} specifies the level of simplification, \texttt{-I} turns on the incremental solving and \texttt{-T} specifies the timeout of Z3-solver in seconds. The default settings is the incremental version of \emph{multi-level} (see Algorithm~\ref{alg:multi}).

\todo{Jake parametry ten tool ma? Co potrebuje k behu? Kde je dostupny? Pod jakou licenci?}

@@

\begin{table}[h]
\caption{LTL to automata translators used for the experimental evaluation
and the number of successfully translated formulas.}
\label{tab:ltltranslators}
\centering
\begin{tabular}{lr@{~~~}lr}
\toprule
tool        & version&homepage & automata \\
\midrule
\texttt{ltl2tgba} & 2.10.4 & \url{https://spot.lrde.epita.fr} & 89\\
\texttt{ltl3tela} & 2.2.0  & \url{https://github.com/jurajmajor/ltl3tela} & 108\\
\texttt{ltl2dela} & 21.0 & \multirow{2}{*}{\url{https://owl.model.in.tum.de/}} & 162\\
\texttt{ltl2dgra} & 21.0 & & 274\\
\bottomrule
\end{tabular}
\end{table}

>>>>

The presented reduction algorithms have been implemented in a tool
called \telatko. The tool is implemented in Python 3 and uses the Spot
library~\cite{duret.16.atva2} for automata parsing and manipulation
and the theorem prover Z3~\cite{demoura.08.tacas} to solve the
satisfiability of QBF formulas. \telatko is available at
\url{https://gitlab.fi.muni.cz/xschwar3/telatko} under the GNU GPLv3
license. The tool can be executed by the command 
\begin{center}
  \texttt{telatko -F <input.hoa> [-L }$j$\texttt{] [-C] [-I] [-T }$t$\texttt{] [-O <output.hoa>]}
\end{center}
where
\begin{description}
\item[\texttt{-F <input.hoa>}] specifies the file with the input automaton in HOA format~\cite{babiak.15.cav}, 
\item[\texttt{-L }$j$] specifies the reduction level; if omitted, the multi-level reduction is used,
\item[\texttt{-C}] switches on the reduction of the number of clauses
  after the number of marks is reduced (it corresponds to
  $\mathit{reduceC}=\true$ in Algortihms~\ref{alg:single}
  and~\ref{alg:multi}),
\item[\texttt{-I}] switches on the incremental version,
\item[\texttt{-T }$t$] sets the timeout for QBF query to $t$ seconds (the default value is 50 seconds), 
\item[\texttt{-O <output.hoa>}] specifies the output file; if omitted,
  the produced automaton is sent to \textit{stdout} in the HOA format.
\end{description}

@@

\begin{table}[h]
\caption{LTL to automata translators used for the experimental evaluation
and the number of successfully translated formulas.}
\label{tab:ltltranslators}
\centering
\begin{tabular}{lr@{~~~}lr}
\toprule
tool        & version&homepage & automata \\
\midrule
\texttt{ltl2tgba} & 2.10.4 & \url{https://spot.lrde.epita.fr} & 89\\
\texttt{ltl3tela} & 2.2.0  & \url{https://github.com/jurajmajor/ltl3tela} \todo{RELEASE} & 108\\
\texttt{ltl2dela} & 21.0 & \multirow{2}{*}{\url{https://owl.model.in.tum.de/}} & 162\\
\texttt{ltl2dgra} & 21.0 & & 274\\
\bottomrule
\end{tabular}
\end{table}
